Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-04 draft/accordionComplexSurfaces.tex

%\begin{figure}[t]
%	\capstart
%	\centerline{\includegraphics[scale=.7]{examplesSurfaces2}}
%	\caption{The surface~$\surface_{\bar Q}$ for the last two quivers~$\bar Q$ of \fref{fig:quivers}. The boundaries of the surfaces are shaded. The first surface is a cylinder, the second one is a torus with a hole.}
%	\label{fig:examplesSurfaces2}
%\end{figure}
%
Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.
Note that we could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
\begin{itemize}
\item consider one $(\ell+1)$-gon~$P_\omega$ for each straight walk~$\omega$ of length~$\ell$ in~$\bar Q$ or in~$\bar Q\koszul$ (just closing~$\omega$ with an additional edge connecting~$t(\omega)$ to~$s(\omega)$),
\item for each arrow~$\alpha \in Q_1\blossom$, consider the only straight walks~$\omega$ of~$\bar Q$ and~$\omega\koszul$ of~$\bar Q\koszul$ containing~$\alpha$, and glue the polygons~$P_\omega$ and~$P_{\omega\koszul}$ along their edges corresponding to~$\alpha$.
\end{itemize}
The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.

>>>>

Definition~\ref{def:surfaceQuiver} constructs an orientable surface~$\surface(\bar Q)$ with boundaries.

\begin{remark}
We could equivalently construct the surface~$\surface_{\bar Q}$ as follows:
\begin{itemize}
\item consider one $(\ell+1)$-gon~$P_\omega$ for each straight walk~$\omega$ of length~$\ell$ in~$\bar Q$ or in~$\bar Q\koszul$ (just closing~$\omega$ with an additional edge connecting~$t(\omega)$ to~$s(\omega)$),
\item for each arrow~$\alpha \in Q_1\blossom$, consider the only straight walks~$\omega$ of~$\bar Q$ and~$\omega\koszul$ of~$\bar Q\koszul$ containing~$\alpha$, and glue the polygons~$P_\omega$ and~$P_{\omega\koszul}$ along their edges corresponding to~$\alpha$.
\end{itemize}
\end{remark}

The advantage of Definition~\ref{def:surfaceQuiver} is that it automatically endows with two disjoint sets~$V_{\bar Q}$ and~${V_{\bar Q}}\dual$ of marked points and two dual dissections~$\dissection_{\bar Q}$ and~${\dissection_{\bar Q}}\dual$ defined as follows.
